---
title: "Yojee - Case"
output: html_notebook
---

Case 1:  A delivery company IParcel delivers packages to certain locations every day. Below is a sample set of the lat and lngs.
•	1 parcel per location for the sake of simplicity
•	There are n number of delivery boys riding motorcycles available

The purpose of this problem is to come up with an efficient path for each of the 25 drivers from a central distribution point (11.552931,104.933636).

Things we expect
•	Code on a git repo
•	Efficiency in running the problem
•	Any visualisation that you can think of
•	Ideas on how you plan to scale this if the number of locations increase (more warehouses and distribution points). Also how this can be translated to engineering infrastructure if need be.
•	Problem statement is purposefully at a very high level. If you have any new ideas we didn’t think of, would be a bonus.

*Please also find the attached sample csv file.

```{r}
# set options and libraries
library("TSP")
library("maps")
library("sp")
library("maptools")

data("USCA50")
data("USCA312")
data("USCA312_map")

setwd(".\\")
options(digits=9)

```


```{r}
# Read source data from locations.csv file
loc.raw <- read.csv(file = "locations.csv", header = TRUE, sep = ",", stringsAsFactors = FALSE)
str(loc.raw)
```

```{r}
# Check first few rows of data
head(loc.raw)
```

```{r}
# Clean dataset, filter invalid records
loc.nan <- loc.raw[(is.na(loc.raw$lon)), ]
loc.nan
```


```{r}
# Check cleaned dataset
loc.new <- loc.raw[(!is.na(loc.raw$lon)), ]
loc.new$lat <- as.numeric(loc.new$lat)
str(loc.new)

```

```{r}
# Function to calculate distance (Euclidean Distance) in kilometers between two points.
# Reference : https://conservationecology.wordpress.com/2013/06/30/distance-between-two-points-in-r/

earth.dist <- function (long1, lat1, long2, lat2){
rad <- pi/180
a1 <- lat1 * rad
a2 <- long1 * rad
b1 <- lat2 * rad
b2 <- long2 * rad
dlon <- b2 - a2
dlat <- b1 - a1
a <- (sin(dlat/2))^2 + cos(a1) * cos(b1) * (sin(dlon/2))^2
c <- 2 * atan2(sqrt(a), sqrt(1 - a))
R <- 6378.145
d <- R * c
return(d)}
```


```{r}
# Define Central Distribution Point location

loc.cdp <- data.frame(lat = 11.552931, lon = 104.933636)
loc.cdp
```


```{r}
# Calculate distance from Central Distribution Point to each delivery location

loc.new$km <- earth.dist(loc.cdp$lon, loc.cdp$lat, loc.new$lon, loc.new$lat)
head(loc.new)
```


```{r}
# Check last few records

tail(loc.new)
```


```{r}
# Check summary of dataset

summary(loc.new)
```

```{r, fig.width=11}
# box and whisker plot for reviewing distribution

boxplot(loc.new[(loc.new$km < 5),], use.cols = TRUE, horizontal = TRUE)
```

```{r}
# TSP solver methods
methods <- c("nearest_insertion", "farthest_insertion", "cheapest_insertion", "arbitrary_insertion", "nn", "repetitive_nn", "two_opt")
```

```{r}
# Tour comparison for 50 US cities.
tours <- sapply(methods, FUN = function(m) solve_TSP(USCA50, method = m),simplify = FALSE)
tours
```

```{r, fig.width=11}
dotchart(sort(c(sapply(tours, tour_length), optimal = 15000)), xlab = "tour length", xlim = c(10000, 25000))
```

```{r}
data("USCA312")
tsp <- insert_dummy(USCA312, label = "cut")
tsp

concorde_path("C:\\Concorde")


# Tour comparison for 313 US cities.
tours <- sapply(methods, FUN = function(m) solve_TSP(tsp, method = m),simplify = FALSE)
tours
```

```{r, fig.width=11}
dotchart(sort(c(sapply(tours, tour_length), optimal = 35000)), xlab = "tour length", xlim = c(30000, 50000))
```
```{r}
mytour <- solve_TSP(tsp, method = "two_opt")
mytour
```
```{r}
path <- cut_tour(mytour, "cut")
head(labels(path))
```
```{r}
tail(labels(path))
```

```{r}
plot_path <- function(path){
plot(as(USCA312_coords, "Spatial"), axes = TRUE)
plot(USCA312_basemap, add = TRUE, col = "gray")
points(USCA312_coords, pch = 3, cex = 0.4, col = "red")
path_line <- SpatialLines(list(Lines(list(Line(USCA312_coords[path,])), ID="1")))
plot(path_line, add=TRUE, col = "black")
points(USCA312_coords[c(head(path,1), tail(path,1)),], pch = 19, col = "black")
}
```

```{r, fig.width=11}
plot_path(path)
```

```{r}
# Vehicle Stop coordinates
veh.stop <- loc.new[1:2]
coordinates(veh.stop) <- c("lon","lat")
summary(veh.stop)

```

